Fail Faster

### 2025-03-22 paper/paper.tex
blah

Our results are summarized in \figref{fig:time}.
Our type-derived \camlname BST generator achieves speedups ranging from $1.08-1.29\times$, which increase
dramatically, to $6.13-9.65\times$, when combined with \csplitmix. The insertion-based BST generator sees
$1.13-1.21\times$ speedups with staging alone, and $4.32-5.36\times$ when also
using \csplitmix. The single-pass BST generator benefits more from
staging, with speedups of $2.31-2.34\times$, rising to $8.61-8.95\times$ when combined with
\csplitmix. 
% We attribute the difference in performance speedup to the fact that
% BST strategies rely on relatively few calls to generator combinator functions,
% but sample extensively from the \rand; notably, single-pass BST, which uses the largest
% number of calls to generator combinators, also sees the greatest benefit from staging. \tr{Call this out earlier? Unless we have the fancy plot.}

For STLC, staging accounts for the bulk of performance gains, yielding
$1.71-2.64\times$ speedups for the type-derived STLC generator and $4.60-5.46\times$ for
the well-typed generator. Adding \csplitmix, these numbers increase to
$2.60-5.15\times$ and $4.83-7.75\times$.

@@

The boolean list generator experiences $3.61-7.10\times$ speedups with
staging, and its performance actually slightly \textit{decreases} when
combined with \csplitmix ($3.43-6.83\times$). This is likely because sampling
booleans is cheap enough that the overhead of crossing the FFI barrier is
greater than that of generating values directly in OCaml.

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.49]{scala.png}
 \caption{Time to generate values of varying sizes using each \scalaname strategy. SC is ScalaCheck; Staged is \scalaname.}
 \label{fig:scala}
 \end{figure}

>>>>

Our results are summarized in \figref{fig:time}.
Our type-derived \camlname BST generator achieves speedups ranging from $1.30-1.38\times$, which increase
dramatically, to $2.13-7.76\times$, when combined with \csplitmix. The insertion-based BST generator sees
$1.18-1.22\times$ speedups with staging alone, and $3.83-6.31\times$ when also
using \csplitmix. The single-pass BST generator benefits more from
staging, with speedups of $2.22-2.25\times$, rising to $9.05-9.82\times$ when combined with
\csplitmix. 
% We attribute the difference in performance speedup to the fact that
% BST strategies rely on relatively few calls to generator combinator functions,
% but sample extensively from the \rand; notably, single-pass BST, which uses the largest
% number of calls to generator combinators, also sees the greatest benefit from staging. \tr{Call this out earlier? Unless we have the fancy plot.}

For STLC, staging accounts for the bulk of performance gains, yielding
$1.73-4.05\times$ speedups for the type-derived STLC generator and $4.10-5.71\times$ for
the well-typed generator. Adding \csplitmix, these numbers increase to
$2.90-5.39\times$ and $5.33-8.33\times$.

@@

The boolean list generator experiences $2.77-7.47\times$ speedups with
staging, and its performance changes very little when
combined with \csplitmix ($2.77-7.57\times$). This is likely because sampling
booleans is cheap enough that the overhead of crossing the FFI barrier is
comparable to that of generating values directly in OCaml.

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.41]{scala.png}
 \caption{Time to generate values of varying sizes using each \scalaname strategy. SC is ScalaCheck; Staged is \scalaname.}
 \label{fig:scala}
 \end{figure}
